### 2019-03-26 5_evaluation.tex
Apply Alex's comments to sections 6 and 7.

For this reason, we feel especially strongly that it is important to
measure the performance behaviors of programming systems under
realistic workloads, rather than trivial dependencies.

>>>>

For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

### 2019-03-26 6_related.tex
Apply Alex's comments to sections 6 and 7.

A common failure mode for mini-apps is to bite off more complexity
than can be reasonably implemented to a level of quality sufficient
for publication. This can lead to publications for mini-apps omitting
implementations or performance results for systems beyond the reference
implementation. Follow-up papers, if any, often compare only against a
reference implementation and omit any other implementations that might
exist.

@@

\item
The mini-app CoMD received a software release but no initial formal
publication. One follow-up paper describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.

@@

Microbenchmarks are often easier to implement, but may not be
representative of real-world applications. From the PRK
suite~\cite{PRK14}, the PRK Stencil code has been reasonably widely
implemented, and a follow-up paper~\cite{PRKRuntimes16} compares MPI
variants, SHMEM, UPC, Charm++, and Grappa. However, PRK Stencil is a
simple code involving 2 kernels (which combined fit in under 50 lines
of C++) and a halo exchange on a structured grid; it is unclear to
what extent this is representative of real-world applications. Other
codes in PRK are even less representative.

The NAS benchmark suite~\cite{NAS91, NAS95} are widely studied with
implementations in OpenMP~\cite{NASOpenMP99}, MPI and
MPI+OpenMP~\cite{NASMPIOpenMP00}, and
Charm++~\cite{NASCharm96}. However the benchmarks consist mostly of small
kernels for dense array computations, and do not generalize to larger
applications.

System-specific benchmarks have been used to quantify specific aspects
of system performance, such as MPI communication or collective
latency~\cite{MPPTest99, MPIBench01}. These measurements typically do
not generalize beyond the immediate system they attempt to quantify,
nor in an obvious way to real-world applications.

>>>>

A common failure mode for mini-apps is to bite off more complexity
than can be reasonably implemented to a level of quality sufficient
for meaningful measurement. New mini-apps often provide only a
reference implementation, or omit performance evaluations of different
implementations, if those are presented. Follow-up experiments, if
any, normally present a single system, and compare against the
reference implementation (or not at all) and not with any other
implementations that might be available. As a result, comparative
studies across many implementations are rare.

@@

\item
One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.

@@

Microbenchmarks are often easier to implement, but may not be
representative of real-world applications. From the PRK
suite~\cite{PRK14}, the PRK Stencil code has been reasonably widely
implemented, and a follow-up paper~\cite{PRKRuntimes16} compares MPI
variants, SHMEM, UPC, Charm++, and Grappa. However, PRK Stencil is a
single, simple code involving 2 kernels (which combined fit in under 50 lines
of C++) and a halo exchange on a structured grid. The NAS benchmark suite~\cite{NAS91, NAS95} are also relatively widely studied with
implementations in OpenMP~\cite{NASOpenMP99}, MPI and
MPI+OpenMP~\cite{NASMPIOpenMP00}, and
Charm++~\cite{NASCharm96}. The benchmarks consist mostly of small
kernels for dense array computations. Neither the PRK nor the NAS
benchmark suite achieve the breadth of coverage, flexibility, or ease
of implementation of Task Bench. We believe the evidence for ease of
implementation is clear; Task Bench is implemented for more systems
than all previous mini-apps and microbenchmarks. Task Bench is also
not a fixed set of benchmarks, and it is even easier to use Task Bench
to generate a new benchmark to measure some aspect of system
performance.

System-specific benchmarks have been used to quantify specific aspects
of system performance, such as MPI communication or collective
latency~\cite{MPPTest99, MPIBench01}. These measurements typically do
not generalize beyond the immediate system they measure.

### 2019-03-26 7_conclusion.tex
Apply Alex's comments to sections 6 and 7.

We presented Task Bench, a parameterized benchmark powerful enough to
enable the exploration of a broad space of application scenarios, but
also simple enough to permit implementation in a wide array of systems
to a level of quality sufficient for comparative study. Our study of
13 programming systems is novel in its breadth, as well as the depth
of insight it delivers about different systems. We discover, among
other things, that the baseline overhead of systems varies by up to 5
orders of magnitude.

Helping us in this endeavor is a new metric, minimum effective task
granularity (METG), which helps to sidestep a number of potential
issues in the evaluation of task scheduling performance, and helps to
separate such factors from changes in communication topology and
latency at increasing scales of the machine.

>>>>

We presented Task Bench, a parameterized benchmark flexible enough to
enable the exploration of a broad space of application scenarios, but
also simple enough to permit implementation in a wide array of systems
to a level of quality sufficient for comparative study. Our study of
13 programming systems is novel in its breadth, as well as the depth
of insight it delivers about different systems. We discover, among
other things, that the baseline overhead of parallel and distributed
programming systems varies by up to 5 orders of magnitude.

Helping us in this endeavor is a new metric, minimum effective task
granularity (METG), which isolates the inherent overhead of the
runtime system for a given application from factors such as changes in
communication topology and latency when using progressively larger
portions of a machine.
